\vspace{-0.5cm}The X-shooter GTO sample of GRB afterglow and host Galaxy spectra

### 2016-11-14 document/XSGRB_sample.tex
Reduction stuff

\section{Introduction}

@@

\subsection{Sample selection criteria and observations}

\subsection{Sample selection criteria} \label{samplecrit}

Being of transient nature, it is difficult to impose strong sample selection
criteria on GRBs, without hampering the follow-up effort. Many natural follow-up
restrictions exists from already, being it weather conditions, pointing
restrictions of the telescope or poorly localized bursts as reported by the
\textit{Swift}-telescope. To maximize the return of the follow-up campaign
we have chosen a few selection criteria that attempts to provide an unbiased
selection of bursts, while allowing for a high success-rate

@@

\subsection{Follow-up procedure}

\subsubsection{RRM observations} \label{RRM}
The rapid-response mode is

\subsection{Observations}
All the observations in this sample has been carried out using the
cross-dispersed echelle spectrograph, X-shooter \citep{Vernet2011}, mounted on
two of the four Unit Telescopes at ESO/VLT, UT2 (Kueyen) and UT3 (Melipal)
during the duration of this follow-up campaign, which covers the entire lifetime
of X-shooter. Observations have been carried out from the ESO period P84
through P98 under the following programme IDs: 098.A-0055, 097.A-0036, 096.A-0079,
095.A-0045, 094.A-0134, 093.A-0069, 092.A-0124, 0091.C-0934, 090.A-0088,
089.A-0067, 088.A-0051, 087.A-0055, 086.A-0073, 085.A-0009 and 084.A-0260.

@@

\section{Data processing}

In this section we describe how the final data products are produced.

@@

\subsection{Post-processing} \label{postproc}

@@

\subsection{Correction for offsets in the wavelength calibration}    \label{wavecal}

Additionally, the wavelength solution for all bursts have been re-calibrated. Using a synthetic sky spectrum \citep{Noll2012, Jones2013}, a first refinement of the wavelength solution have been obtained by cross-correlating with the observed sky. 
Both a multiplicative and an additive offset has been tested, but in terms of $\chi^2$, the model with only a multiplicative offset is preferred.

X-shooter, being installed at the VLT Cassegrain focus is  prone to
flexures during operations. The flexures modify the projection of the slit
on the detector with respect to the one obtained in daytime calibration. 
This require a modification of the wavelength solution in order to
process correctly the night-time data. Part of this correction
is performed by the pipeline using the frames taken
during X-shooter Active Flexure Compensation procedure
\footnote{X-shooter User Manual available at https://www.eso.org/sci/facilities/paranal/instruments/xshooter/doc.html}
We corrected the remaining part using as a reference the sky
emission lines present in the observed data.

For every afterglow observation we reduced one frame individually in STARE mode without
sky subtraction obtaining $\sim$ 100 sky spectra. The sky line list compiled at ESO for
the E-ELT
study\footnote{http://www.eso.org/sci/facilities/eelt/science/drm/tech\_data/data/optical\_ir\_sky\_lines.dat}
from the work of (Hanuschik, 2003, A\&A, 407, 1157) and (Rousselot et al. (2000, A\&A, 354, 1134), was used as a reference.
From this list, we selected a subset of bright and isolated lines. In the case of the OH doublets, unresolved at X-shooter resolution, we took as line position the average between the blue and red components. To find the offsets of the spectra, we fitted gaussians near the
expected positions under IDL using the MPFIT software (Markwardt, 2009, Astronomical Society of the Pacific Conference Series, Vol. 411, ADASS XVII, ed. D.A. Bohlender, D. Durand, \& P. Dowler, 251) and we compared the result to the tabulated values.
The resulting offsets, which were smaller than 0.1 \AA~in the UVB and VIS data
and smaller than 0.5 \AA~in the NIR spectra, were applied to the corresponding spectra.

\subsection{Spectral extraction}    \label{extract}

@@

\subsection{Spectral resolution} \label{resolution}
The afterglow spectra described in this paper are obtained in
Target-of-Opportunity (override) mode.
In most cases there is therefore little possibility to tweak slit widths to the
seeing at the time of observations (i.e. to optimise spectral resolution and
signal to noise), and almost all our data is therefore taken with a fixed set
of slit widths and binning, described above.
In a fair number of cases, the seeing full width at half maximum (FWHM) is
considerably smaller than the silt width, and the delivered spectral resolution
will then be determined by the seeing rather than slit width, as afterglows are
point sources (this is evidently not the case for extended sources, e.g for
host galaxies).
The delivered resolution for slit width dominated spectra post-reduction and
extraction can easily be determined from the bright sky emission lines.
For afterglow spectra with very high signal to noise, the delivered spectral
resolution can at times be determined from the science data themselves.
However, in the presence of multiple velocity components in absorption, other
forms of line broadening, and a lack of lines at some redshifts, this is
difficult to do at poorer signal to noise ratios (the majority of spectra in
our sample).
A broad starting value for the expect resolution will help fitting of these
spectra, and can be important in upper limit determination, and for this reason
we construct a aim to construct a crude relation between the seeing and the
delivered resolution at our slit width, binning, and reduction pipeline
settings.
To this end we use observations of telluric standard stars that are taken with
identical instrument settings as our afterglow spectra, usually just after the
science data, as part of the ESO X-shooter calibration plan.
These spectra have been reduced together with the afterglow spectra, using
identical pipeline settings with the same version of the pipeline.
First we fit a Gaussian function in the spatial direction of the trace of the
standard star at 792 nm (i.e. in the VIS arm).
After this, we fit a series of  20 telluric absorption lines in the telluric
standard star spectra with Gaussians, taking care to select transitions that
are not almost-resolved multiples, should be intrinsically unresolved, and are
in areas with well defined continuum flux.
We pick 34 telluric standard stars spanning a range of DIMM seeing values, with
the majority between $0.5-1.5 arcsec$.
The resulting distribution of spectral FWHM (km/s) as a function of spatial
FWHM at 792 nm is fairly well described by a linear relation $a + b*x$, with
$x$ the spatial FWHM in pixels (with 0.15 arc sec per pixel),  $a= 21.4 \pm
1.3$ km/s, $b=1.4 \pm 0.2$.
We use this linear relation as a way to estimate the spectral resolution for
medium to poor signal to noise afterglow spectra in the VIS arm.
To extend this to the UVB and NIR arm, we measured a series of lines in NIR arm
spectra of a subset of 19 sources used for the VIS arm above, and find that the
resulting distribution is consistent with a simple scaling of the VIS arm
relation by the ratio of resolutions of the NIR and VIS arm for unresolved,
slit filling, sources as given on the ESO instrument website.
The UVB arm contains no suitable absorption lines to use, and we therefore use
a scaled value as in the NIR arm.
While this simple method is not terribly accurate (for one, the spatial profile
of the trace is not a perfect Gaussian), but it gives a sufficiently accurate
estimate for the analysis of these poor signal to noise science spectra.

@@

\section{Results}
\input{tables/burst_overview.tex}

\subsection{Complete sample}

\subsection{Follow-up timing and afterglow brightness}
This sections should contain a plot og the follow-up delay and the acquisition image brightness at the time of observations.

\subsection{Properties of rejected triggers} \label{badbursts}
How many bursts have been excluded due to particularities in the follow-up attempt. Visitor, Weather, technical issues.

\subsection{On the nature of triggered GRBs without detected optical afterglow.}
This should include observations where the acquisition image has been taken, but observations were discontinued due to non-detection. What are the X-ray properties of these bursts?

\subsection{Redshifts}

\subsubsection{Afterglow-based redshifts}

\subsubsection{Emissionline-based redshifts}	
Redshift completeness

\subsection{Hydrogen column densities}

\section{Discussion}

\subsection{Comparison to previous samples.}	
This should also include a discussion of dark bursts. 
Cuchiara. BAT6 (Salvaterra), TOUGH

\subsection{Comparison to previous samples.}

\subsection{X-ray column densities vs. optically derived ones}

@@

\subsection{Why is the HI column truncated?}

@@

\section{Conclusion}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sample selection criteria and observations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sample selection criteria} \label{samplecrit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Being of transient nature, it is difficult to impose strong sample selection
criteria on GRBs, without hampering the follow-up effort. Many natural follow-up
restrictions exists from already, being it weather conditions, pointing
restrictions of the telescope or poorly localized bursts as reported by the
\textit{Swift}-telescope. To maximize the return of the follow-up campaign
we have chosen a few selection criteria that attempts to provide an unbiased
selection of bursts, while allowing for a high success-rate

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Follow-up procedure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{RRM observations} \label{RRM}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The rapid-response mode is

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Observations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

All the observations in this sample has been carried out using the
cross-dispersed echelle spectrograph, X-shooter \citep{Vernet2011}, mounted on
two of the four Unit Telescopes at ESO/VLT, UT2 (Kueyen) and UT3 (Melipal)
during the duration of this follow-up campaign, which covers the entire lifetime
of X-shooter. Observations have been carried out from the ESO period P84
through P98 under the following programme IDs: 098.A-0055, 097.A-0036, 096.A-0079,
095.A-0045, 094.A-0134, 093.A-0069, 092.A-0124, 0091.C-0934, 090.A-0088,
089.A-0067, 088.A-0051, 087.A-0055, 086.A-0073, 085.A-0009 and 084.A-0260.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data processing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In this section we describe how the final data products are produced and
subsequently post-processed. All post-processing scripts developed for this
dataset are made publicly available at
\url{https://github.com/jselsing/XSGRB_reduction_scripts}, along with
instructions of use.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Post-processing} \label{postproc}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

By STARE reducing all observations we additionally get a spectrum of the sky,
which we can use to calibrate the wavelength solution in Sect. \ref{wavecal}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Correction for offsets in the wavelength calibration}    \label{wavecal}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

X-shooter, being installed at the VLT Cassegrain focus is  prone to flexures
during operations. The flexures modify the projection of the slit on the
detector with respect to the one obtained in daytime calibration. This requires a
modification of the wavelength solution in order to process correctly the
night-time data. Part of this correction is performed by the pipeline using the
frames taken during X-shooter Active Flexure Compensation procedure
\footnote{X-shooter User Manual available at
	https://www.eso.org/sci/facilities/paranal/instruments/xshooter/doc.html}.

The remaining offset is corrected by cross-correlation with a synthetic sky
spectrum \citep{Noll2012, Jones2013}. To get the correct seeing PSF with which
to convolve the synthetic sky an initial refinement of the wavelength solution
have been obtained by cross-correlating the observed sky with an unconvolved
synthetic sky. This preliminary wavelength calibration is applied to the
observed sky. The synthetic spectrum is then convolved with an increasing seeing
PSF and the width that minimizes $\chi^2$ with the updated observed sky is
chosen to be the effective sky-PSF. Using the synthetic sky with the matched
resolution, a final wavelength calibration can then be calculated by
cross-correlating the observed sky with the correctly broadened sky spectrum, as
a function of a velocity offset. Both a multiplicative and an additive offset to
the wavelength calibration has been tested, but in terms of $\chi^2$, the model
with only a multiplicative offset is preferred.

The resulting offsets, which were smaller than 0.1 \AA~in the UVB and VIS data
and smaller than 0.5 \AA~in the NIR spectra, but changing over short period of
time were applied to the corresponding spectra.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spectral extraction}    \label{extract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Spectral resolution} \label{resolution}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The afterglow spectra described in this paper are obtained in
Target-of-Opportunity (override) mode.
In most cases there is therefore little possibility to tweak slit widths to the
seeing at the time of observations (i.e. to optimise spectral resolution and
signal to noise), and almost all our data is therefore taken with a fixed set
of slit widths and binning, described above.
In a fair number of cases, the seeing full width at half maximum (FWHM) is
considerably smaller than the silt width, and the delivered spectral resolution
will then be determined by the seeing rather than slit width, as afterglows are
point sources (this is evidently not the case for extended sources, e.g for
host galaxies).
The delivered resolution for slit width dominated spectra post-reduction and
extraction can easily be determined from the bright sky emission lines.
For afterglow spectra with very high signal to noise, the delivered spectral
resolution can at times be determined from the science data themselves.
However, in the presence of multiple velocity components in absorption, other
forms of line broadening, and a lack of lines at some redshifts, this is
difficult to do at poorer signal to noise ratios (the majority of spectra in
our sample).
A broad starting value for the expect resolution will help fitting of these
spectra, and can be important in upper limit determination, and for this reason
we construct a aim to construct a crude relation between the seeing and the
delivered resolution at our slit width, binning, and reduction pipeline
settings.
To this end we use observations of telluric standard stars that are taken with
identical instrument settings as our afterglow spectra, usually just after the
science data, as part of the ESO X-shooter calibration plan.
These spectra have been reduced together with the afterglow spectra, using
identical pipeline settings with the same version of the pipeline.
First we fit a Gaussian function in the spatial direction of the trace of the
standard star at 792 nm (i.e. in the VIS arm).
After this, we fit a series of  20 telluric absorption lines in the telluric
standard star spectra with Gaussians, taking care to select transitions that
are not almost-resolved multiples, should be intrinsically unresolved, and are
in areas with well defined continuum flux.
We pick 34 telluric standard stars spanning a range of DIMM seeing values, with
the majority between $0.5-1.5 arcsec$.
The resulting distribution of spectral FWHM (km/s) as a function of spatial
FWHM at 792 nm is fairly well described by a linear relation $a + b*x$, with
$x$ the spatial FWHM in pixels (with 0.15 arc sec per pixel),  $a= 21.4 \pm
1.3$ km/s, $b=1.4 \pm 0.2$.
We use this linear relation as a way to estimate the spectral resolution for
medium to poor signal to noise afterglow spectra in the VIS arm.
To extend this to the UVB and NIR arm, we measured a series of lines in NIR arm
spectra of a subset of 19 sources used for the VIS arm above, and find that the
resulting distribution is consistent with a simple scaling of the VIS arm
relation by the ratio of resolutions of the NIR and VIS arm for unresolved,
slit filling, sources as given on the ESO instrument website.
The UVB arm contains no suitable absorption lines to use, and we therefore use
a scaled value as in the NIR arm.
While this simple method is not terribly accurate (for one, the spatial profile
of the trace is not a perfect Gaussian), but it gives a sufficiently accurate
estimate for the analysis of these poor signal to noise science spectra.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{tables/burst_overview.tex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Complete sample}	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Follow-up timing and afterglow brightness}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This sections should contain a plot og the follow-up delay and the acquisition image brightness at the time of observations.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Properties of rejected triggers} \label{badbursts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

How many bursts have been excluded due to particularities in the follow-up attempt. Visitor, Weather, technical issues.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{On the nature of triggered GRBs without detected optical afterglow.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This should include observations where the acquisition image has been taken, but observations were discontinued due to non-detection. What are the X-ray properties of these bursts?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Redshifts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Afterglow-based redshifts}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsubsection{Emissionline-based redshifts}	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Redshift completeness

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Hydrogen column densities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Comparison to previous samples.}	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This should also include a discussion of dark bursts. 
Cuchiara. BAT6 (Salvaterra), TOUGH

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%	
\subsection{Comparison to previous samples.}		
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{X-ray column densities vs. optically derived ones}	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Why is the HI column truncated?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
